Boosting, Sparsity, and Conditional Gradient: A Tutorial

### 2014-02-18 arXiv/paper.tex
updated title, abstract

\documentclass[reqno,oneside,a4paper]{amsart}
\usepackage{import, subfiles}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{chngpage}
\input{latex-defs.tex}

@@

\title{Conjugate Gradient, Boosting, and Herding: \\ 
	   Connections and Application}

@@

\begin{abstract} 
Much has been learned about herding since it was first proposed.
We introduce a unifying framework for understanding herding and 
related algorithms. The framework is based on a pair of optimization 
algorithms that we call primal and dual boosted mirror descent.
We define two classes of generalized herding algorithms, 
including one for infinite dimensional spaces
that may apply even when herding does not. A number 
of convergence bounds that apply to herding and generalized
herding are obtained. Along the way we provide
a more cohesive picture of the connections between herding, 
conditional gradient descent, and maximum entropy. 
\end{abstract}

@@

\bibliography{herding}
\bibliographystyle{icml2014}

>>>>

\documentclass[reqno,oneside,a4paper]{amsart}
\usepackage{import, subfiles}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{chngpage}
\usepackage{fullpage}
\input{latex-defs.tex}

@@

\title{Boosting, Sparsity, and Conditional Gradient: A Tutorial}
%Conjugate Gradient, Boosting, and Herding: \\ 
%	   Connections and Application}

@@

\begin{abstract} 
Many recent papers in machine learning and theoretical computer science have 
focused on the idea of sparse or low-rank ``approximations'' to some object: 
for instance, graph sparsification \cite{?}, low-rank SDP approximation \cite{?}, 
and pseudosampling \cite{?}. In this paper we show that, whenever presented with 
a strongly convex optimization problem whose dual problem is linear, we can obtain 
sparse approximate solutions, and use this to re-derive many of the known 
sparsification results.
% Much has been learned about herding since it was first proposed.
% We introduce a unifying framework for understanding herding and 
% related algorithms. The framework is based on a pair of optimization 
% algorithms that we call primal and dual boosted mirror descent.
% We define two classes of generalized herding algorithms, 
% including one for infinite dimensional spaces
% that may apply even when herding does not. A number 
% of convergence bounds that apply to herding and generalized
% herding are obtained. Along the way we provide
% a more cohesive picture of the connections between herding, 
% conditional gradient descent, and maximum entropy. 
\end{abstract}

@@

\bibliography{herding}
\bibliographystyle{plainnat} %icml2014}
